What's in a name? On the automated topic naming of software maintenance activities

### 2010-03-06 icpc/icpc2010.tex
related work edits

Binary Relevance (BR), Calibrated Label Ranking (CLR) and Hierarchy Of Multilabel classifiERs (HOMER), performed the best. HOMER and BR acts as a hierarchy of learners, BR is flat while HOMER tries to build a deeper hierarchy in order to build a more accurate learner~\cite{mulan}. We feel that these classifiers performed better because they have the best micro and macro ROC scores than the other classifiers.

@@

Part of our effort with this project is to understand the qualitative and intentional aspects of requirements in software evolution, a notion we first discussed in \cite{ernst07icsm}. That idea is derived from, in part, work on narratives of software systems shown in academic work like \cite{anton01}, or more general-purpose works like \cite{waldo93}.

@@

Cleland-Huang and her colleagues published work on mining requirements documents for non-functional requirements (quality requirements) in \cite{Cleland-Huang2006}. One approach they tried was similar to this one, with keywords mined from NFR catalogues found in~\cite{chung99}. They managed recall of 80\% with precision of 57\% for the Security NFR, but could not find a reliable source of keywords for other NFRs. Instead, they developed a supervised classifier by using human experts to identify an NFR training set. There are several reasons we did not follow this route. One, we believe we have a more comprehensive set of terms due to the taxonomy we chose. Secondly, we wanted to compare across projects. Their technique was not compared across different projects and the applicability of the training set to different corpora is unclear. A common taxonomy allows us to make inter-project comparison (subject to the assumption that all projects conceive of these terms in the same way). Thirdly, while the objective of Cleland-Huang's study was to identify new NFRs (for system development) our study assumes these NFRs are latent in the textual documents of the project. Finally, the source text we use is less structured than their requirements documents.

Mockus and Votta studied a large-scale industrial change-tracking system in ~\cite{Mockus00}. They also leveraged Wordnet, but only for word roots. They felt the synonyms would be non-specific and cause errors. A nice contribution was access to system developers, with whom they could validate their labels. Since we try to bridge different organizations, these interviews are infeasible (particularly in the distributed world of open-source software).

The other approach is to start with code repositories, and try to extract concerns from there. In \cite{marcus04wcre}, the authors describe their use of Latent Semantic Indexing to identify commonly occurring concerns for software maintenance. Some results were interesting, but their precision was quite low. ConcernLines~\cite{treude09cl} shows tag occurrence using color intensity. They mined change request tags (such as `milestone 3') and used these to make evolutionary analyses of a single product. The presence of a well-maintained set of tags is obviously essential to the success of this technique.
%We maintain that these results require more substantive manipulation before being reported to, for example, management. Like any large-scale data analysis project, it requires skill to derive the implications. Hooking the backend results directly to a reporting tool is unlikely to produce useful results.

% There has been an explosion of interest in mining OSS repositories. Godfrey and Tu \cite{godfrey00} were among the first to use this data to assess software evolution. They discussed how well the growth of Linux was predicted by laws that Lehman and colleagues \cite{lehman85} proposed. More recently, Herraiz et al. \cite{herraiz07icsm} predicted OSS growth using time series analysis. Like us, they refer to release windows as a useful unit of analysis.

Mens et al. \cite{mens08icsm} conducted an empirical study of Eclipse, the OSS code editor, to verify the claims of Lehman~\cite{lehman97sms}. They concerned themselves with source code only, and found Law Seven, ``Declining Quality'', to be too difficult to assess: ``[we lacked an] appropriate measurement of the evolving quality of the system as perceived by the users \cite[p. 388]{mens08icsm}''. This paper examines the notions of quality in terms of a consistent ontology, as Mens et al. call for in their conclusions.

In \cite{Mei2007}, the authors use context information to automatically name topics. They describe probabilistic labeling, using the frequency distribution of words in a topic to create a meaningful phrase. They do not use external domain-specific information as we do.

Massey~\cite{massey02icse} and Scacchi (\cite{scacchi02,scacchi05b}) looked at the topic of requirements in open-source software. Their work discusses the source of the requirements and how they are used in the development process. German~\cite{german03gnome} looked at GNOME specifically, and listed several sources for requirements: leader interest, mimicry, brainstorming, and prototypes. None of this work  addressed quality requirements in OSS, nor did it examine requirements trends.

@@

Most of this related research examined project source code. Software mining of other project corpora is less common. Similarities exist with approaches that begin with structured taxonomies, as with the Hismo software ontology \cite{girba06}. Rigby and Hassan \cite{rigby07msr} used a general purpose taxonomy to classify developer email according to temperament.

>>>>

We have presented the results of Mulan's multi-label learners in Table \ref{tab:mulan}.
Binary Relevance (BR), Calibrated Label Ranking (CLR) and Hierarchy Of Multilabel classifiERs (HOMER), performed the best. HOMER and BR acts as a hierarchy of learners, BR is flat while HOMER tries to build a deeper hierarchy in order to build a more accurate learner~\cite{mulan}. We feel that these classifiers performed better because they have the best micro and macro ROC scores than the other classifiers.

@@

Part of our effort with this project is to understand the qualitative and intentional aspects of requirements in software evolution, a notion we first discussed in \cite{ernst07icsm}. That idea is derived from, in part, work on narratives of software systems shown in academic work from Ant\'{o}n et al.~\cite{anton01}, or more general-purpose work from Waldo~\cite{waldo93}.

@@

Cleland-Huang and her colleagues published work on mining requirements documents for non-functional requirements (NFR) (quality requirements)~\cite{Cleland-Huang2006}. One approach they tried was similar to this one, with keywords mined from NFR catalogues found in their previous work~\cite{chung99}. They managed recall of 80\% with precision of 57\% for the Security NFR, but could not find a reliable source of keywords for other NFRs. Instead, they developed a supervised classifier by using human experts to identify an NFR training set. There are several reasons we did not follow this route. One, we believe we have a more comprehensive set of terms due to the taxonomy we chose. Secondly, we wanted to compare across projects. Their technique was not compared across different projects and the applicability of the training set to different corpora is unclear. A common taxonomy allows us to make inter-project comparison (subject to the assumption that all projects conceive of these terms in the same way). Thirdly, while the objective of Cleland-Huang's study was to identify new NFRs (for system development) our study assumes these NFRs are latent in the textual documents of the project. Finally, the source text we use is less structured than their requirements documents.

In the same vein, Mockus and Votta~\cote{Mockus00} studied a large-scale industrial change-tracking system. They also leveraged Wordnet, but only for word roots. They felt the synonyms would be non-specific and cause errors. A nice contribution was access to system developers, with whom they could validate their labels. Since we try to bridge different organizations, these interviews are infeasible (particularly in the distributed world of open-source software).

The other approach is to start with code repositories, and try to extract concerns from there. Marcus et al.~\cite{marcus04wcre} describe their use of Latent Semantic Indexing to identify commonly occurring concerns for software maintenance. Some results were interesting, but their precision was quite low. ConcernLines~\cite{treude09cl} shows tag occurrence using color intensity. They mined change request tags (such as `milestone 3') and used these to make evolutionary analyses of a single product. The presence of a well-maintained set of tags is obviously essential to the success of this technique.
\begin{comment}
%We maintain that these results require more substantive manipulation before being reported to, for example, management. Like any large-scale data analysis project, it requires skill to derive the implications. Hooking the backend results directly to a reporting tool is unlikely to produce useful results.

% There has been an explosion of interest in mining OSS repositories. Godfrey and Tu \cite{godfrey00} were among the first to use this data to assess software evolution. They discussed how well the growth of Linux was predicted by laws that Lehman and colleagues \cite{lehman85} proposed. More recently, Herraiz et al. \cite{herraiz07icsm} predicted OSS growth using time series analysis. Like us, they refer to release windows as a useful unit of analysis. 
\end{comment}

Mens et al.~\cite{mens08icsm} conducted an empirical study of Eclipse, the open source software (OSS) source code editor, to verify the claims of Lehman~\cite{lehman97sms}. They concerned themselves with source code only, and found Law Seven, ``Declining Quality'', to be too difficult to assess: ``[we lacked an] appropriate measurement of the evolving quality of the system as perceived by the users \cite[p. 388]{mens08icsm}''. This paper examines the notions of quality in terms of a consistent ontology, as Mens et al. call for in their conclusions.

Mei et al.~\cite{Mei2007} use context information to automatically name topics. They describe probabilistic labeling, using the frequency distribution of words in a topic to create a meaningful phrase. They do not use external domain-specific information as we do.

Massey~\cite{massey02icse} and Scacchi~\cite{scacchi02,scacchi05b} looked at the topic of requirements in open-source software. Their work discusses the source of the requirements and how they are used in the development process. German~\cite{german03gnome} looked at GNOME specifically, and listed several sources for requirements: leader interest, mimicry, brainstorming, and prototypes. None of this work  addressed quality requirements in OSS, nor did it examine requirements trends.

@@

Most of this related research examined project source code. Software mining of other project corpora is less common. Similarities exist with approaches that begin with structured taxonomies, as with the Hismo software ontology~\cite{girba06}. Rigby and Hassan~\cite{rigby07msr} used a general purpose taxonomy to classify developer email according to temperament.
